Proposal to improve BBC Search through the use of Linked Data

### 2014-04-30 paper.tex
Some more work on the second chapter.

$$F_\beta = (1 + \beta^2) \cdot \frac{\mathrm{precision} \cdot \mathrm{recall} }{ \beta^2 \cdot \mathrm{precision} + \mathrm{recall}}$$

@@

\section{Linked Data Principles}

@@

@@

These efforts are not as structured and rich as the more notable uses
of semantic web technologies on the programmes microsites, Nature and BBC
Music \cite{}, but indicate that some level of metadata can be retrieved
as linked data. In cases where the metadata are rich enough, it might be
possible to avoid direct integration with databases, hidden back end
web services and other structured ``feeds'' typically set up for enterprise
integration.

>>>>

\begin{displaymath}
  F_\beta = (1 + \beta^2) \cdot \frac{\mathrm{precision} \cdot \mathrm{recall} }{ \beta^2 \cdot \mathrm{precision} + \mathrm{recall}}
\end{displaymath}

@@

@@

It can be seen as a subset of Semantic Web techniques and it builds upon
the \emph{Resource Description Framework} (RDF)\cite{lassila1999resource},
which is a general-purpose method for describing and modelling information.

In this chapter, I will outline how web authors are encouraged to publish
linked data within their content and how that is already used to enhance
search results in global search engines. I will then introduce how linked
data may be used within an enterprise setting to reduce traditional
integration efforts and then touch on some other aspects of the linked
data domain that could be of interest to the search application.

\section{Publishing Linked Data within Web Pages}

The Semantic Web movement has long recommended an approach of embedding
RDF data models within web pages and documents using RDFa\cite{adida2012rdfa}
and RDFa Lite\cite{lite2004rdfa}.

\section{Enhancing Search Engine Results}

@@

These efforts are not as structured and rich as the more notable uses
of semantic web technologies on the programmes microsites, Nature and BBC
Music \cite{raimond2010use}, but indicate that some level of metadata
can be retrieved
as linked data. In cases where the metadata are rich enough, it might be
possible to avoid direct integration with databases, hidden back end
web services and other structured ``feeds'' typically set up for enterprise
integration.

\section{Reasoning and Inference}
